---
title: "P8105_HW3_yz4188"
author: "Yueran Zhang"
date: "19/10/2021"
output: github_document
---

```{r setup}
library(p8105.datasets)
library(tidyverse)
library(p8105.datasets)
library(tidyverse)
library(dplyr)
library(readxl)
library(ggplot2)
library(forcats)
```


## Problem 1

## Load data
```
data("instacart")
```

The data has `r nrow(instacart)` observations, and `r ncol(instacart)` columns.
Totally `r (nrow(instacart)*ncol(instacart))` data points. 
Key variables: One observation is one product from a single order, using `order_id` and `product_id` to identify one observation.
For example, providing order_id=1 and product_id=49302 will select the first row of the original table.
Aisle is a key variable to do analysis based on aisle of each single observation.

## How many aisles are there, and which aisles are the most items ordered from?
```{r aisles}
aisles = instacart %>% 
  count(aisle) %>% 
  arrange(desc(n))
```
There are `r nrow(aisles)` aisles,
`r head(aisles[,1],1)` is the most items ordered from.

## Make a plot that shows the number of items ordered in each aisle
```{r q1_plot1}
instacart %>% 
  count(aisle) %>% 
  mutate(aisle = fct_reorder(aisle, n, .desc=TRUE)) %>%
  filter(n > 10000) %>% 
  ggplot(aes(x = aisle, y = n)) +
  geom_point() + 
  theme(axis.text.x = element_text(angle = 90))
```

## Make a table showing the three most popular items in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits”. Include the number of times each item is ordered in your table.
```{r q1_table1}
instacart %>%
  filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>%
  group_by(aisle) %>% 
  count(product_name) %>%
  mutate(rank = min_rank(desc(n))) %>% 
  filter(rank <= 3) %>%
  arrange(aisle,rank) %>%
  knitr::kable()
```

## Make a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week; format this table for human readers (i.e. produce a 2 x 7 table).
```{r q1_table2, message = FALSE}
instacart %>%
  filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>%
  group_by(product_name,order_dow) %>%
  summarize(mean = mean(order_hour_of_day)) %>%
  pivot_wider(
    names_from = order_dow, 
    values_from = mean)%>%
  knitr::kable()
```

## Problem 2
## Data Cleaning
```{r brfss}
data("brfss_smart2010")
brfss = brfss_smart2010 %>%
  janitor::clean_names() %>%
  filter(topic == "Overall Health", response %in% c("Excellent","Good","Very good","Fair","Poor")) %>%
  arrange(factor(response, levels = c("Poor","Fair","Good","Very good","Excellent")))
```

## In 2002, which states were observed at 7 or more locations? What about in 2010?
In 2002:
```{r brfss_2002}
brfss_2002 = brfss %>%
  filter(year == 2002) %>%
  select(locationabbr, locationdesc) %>%
  distinct() %>%
  group_by(locationabbr) %>%
  filter(n() >= 7) %>%
  select(locationabbr) %>%
  distinct() %>%
  knitr::kable()
brfss_2002
```
In 2010:
```{r brfss_2010}
brfss_2010 = brfss %>%
  filter(year == 2010) %>%
  select(locationabbr, locationdesc) %>%
  distinct() %>%
  group_by(locationabbr) %>%
  filter(n() >= 7) %>%
  select(locationabbr) %>%
  distinct() %>%
  knitr::kable()
brfss_2010
```
The results shows that in 2010, there are more states were observed at 7 or more locations than 2002.

## Construct a dataset that is limited to Excellent responses, and contains, year, state, and a variable that averages the data_value across locations within a state. Make a “spaghetti” plot of this average value over time within a state.
```{r q2_plot1}
brfss %>%
  filter(response %in% "Excellent") %>%
  select(year, locationabbr, data_value) %>%
  na.omit() %>%
  unique() %>%
  group_by(locationabbr, year) %>%
  mutate(avg = mean(data_value)) %>%
  select(year, locationabbr, avg) %>%
  distinct() %>%
  ggplot(aes(x = year, y = avg)) +
  geom_line(aes(group = locationabbr, color = locationabbr)) +
  labs(
    title = "Average data value over time within each states",
    x = "Year",
    y = "Average Data Value") +
  guides(col=guide_legend("State"))
```

According to the plot, the average data value for each state drops overtime.

## Make a two-panel plot showing, for the years 2006, and 2010, distribution of data_value for responses (“Poor” to “Excellent”) among locations in NY State.
```{r q2_plot2}
brfss %>%
  filter(year %in% c(2006,2010), locationabbr == "NY") %>%
  ggplot(aes(x = data_value, fill = response)) +
  geom_density()+
  facet_grid(cols = vars(year))
```

According to the plot, the range of data value for each kind's of response in 2010 is wider than the one in 2006. 

## Proplem 3

## Load Data
```{r}
accel = read_csv("data/accel_data.csv") %>%
  janitor::clean_names() %>% 
  mutate(weekday_weekend = recode(day,"Monday" = "weekday",
                                     "Tuesday"= "weekday",
                                     "Wednesday" = "weekday",
                                     "Thursday" = "weekday",
                                     "Friday" = "weekday",
                                     "Saturday" = "weekend",
                                     "Sunday" = "weekend",
                                    ))%>%
  select(day_id, week, day, weekday_weekend, everything()) %>%
  pivot_longer(
    activity_1 : activity_1440,
    names_prefix = "activity_",
    names_to = "activity",
    values_to = "activity_count"
  ) %>% 
  rename(minute = activity)
```

Exiting variables are: `r colnames(accel)`.
There are `r nrow(accel)` observations.

## Traditional analyses of accelerometer data focus on the total activity over the day. 
```{r q3_table1}
accel %>% 
  group_by(day_id, week, day) %>% 
  summarize(total = sum(activity_count)) %>% 
  knitr::kable()
```

According to the table, the total activity count on Saturday drops apparently.

## Accelerometer data allows the inspection activity over the course of the day.
```{r q3_plot1}
accel %>% 
  ggplot(aes(x = as.numeric(minute), y = activity_count, color = day)) + 
  geom_line() +
  labs(
    title = "24-hour activity time courses for each day ",
    x = "Time",
    y = "Activity Count"
  ) +
  scale_x_continuous(
    limits = c(0, 1440),
    breaks = c(0, 240, 480, 720, 960, 1200, 1440), 
    labels = c("12am", "4am", "8am", "12pm", "4pm", "8pm", "12am")
  )
```

According to the graph, the activity counts goes lower after 10pm.
In each day, activity counts are highter at near 8am, 12pm, 4pm, and 8pm.